% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}

% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
        \begin{center}
        \vspace*{1.0cm}

        \Huge
        {\bf Cross-Domain Sentence Modeling for Relevance Transfer with BERT}

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Zeynep Akkalyoncu Yilmaz \\

        \vspace*{3.0cm}

        \normalsize
        A thesis \\
        presented to the University of Waterloo \\ 
        in fulfillment of the \\
        thesis requirement for the degree of \\
        Master of Mathematics \\
        in \\
        Computer Science \\

        \vspace*{2.0cm}

        Waterloo, Ontario, Canada, 2019 \\

        \vspace*{1.0cm}

        \copyright\ Zeynep Akkalyoncu Yilmaz 2019 \\
        \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.

 
% E X A M I N I N G   C O M M I T T E E (Required for Ph.D. theses only)
% Remove or comment out the lines below to remove this page
%\begin{center}\textbf{Examining Committee Membership}\end{center}
%  \noindent
%The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.
%  \bigskip
%  
%  \noindent
%\begin{tabbing}
%Internal-External Member: \=  \kill % using longest text to define tab length
%External Examiner: \>  Bruce Bruce \\ 
%\> Professor, Dept. of Philosophy of Zoology, University of Wallamaloo \\
%\end{tabbing} 
%  \bigskip
%  
%  \noindent
%\begin{tabbing}
%Internal-External Member: \=  \kill % using longest text to define tab length
%Supervisor(s): \> Doris Johnson \\
%\> Professor, Dept. of Zoology, University of Waterloo \\
%\> Andrea Anaconda \\
%\> Professor Emeritus, Dept. of Zoology, University of Waterloo \\
%\end{tabbing}
%  \bigskip
%  
%  \noindent
%  \begin{tabbing}
%Internal-External Member: \=  \kill % using longest text to define tab length
%Internal Member: \> Pamela Python \\
%\> Professor, Dept. of Zoology, University of Waterloo \\
%\end{tabbing}
%  \bigskip
%  
%  \noindent
%\begin{tabbing}
%Internal-External Member: \=  \kill % using longest text to define tab length
%Internal-External Member: \> Deepa Thotta \\
%\> Professor, Dept. of Philosophy, University of Waterloo \\
%\end{tabbing}
%  \bigskip
%  
%  \noindent
%\begin{tabbing}
%Internal-External Member: \=  \kill % using longest text to define tab length
%Other Member(s): \> Leeping Fang \\
%\> Professor, Dept. of Fine Art, University of Waterloo \\
%\end{tabbing}

\cleardoublepage

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
 \begin{center}\textbf{Author's Declaration}\end{center}
  \noindent
I hereby declare that I am the sole author of this thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.

  \bigskip
  
  \noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage

% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}
Standard bag-of-words term-matching techniques in document retrieval fail to exploit rich semantic information embedded in the document texts.
One promising recent trend in facilitating context-aware semantic matching has been the development of massively pretrained deep transformer models, culminating in BERT as their most popular example today.
In this work, we propose adapting BERT as a neural re-ranker for document retrieval to achieve large improvements on news articles.
Two fundamental issues arise in applying BERT to ``ad hoc'' document retrieval on newswire collections:\
relevance judgments in existing test collections are provided only at the document level, and documents often exceed the length that BERT was designed to handle.
To overcome these challenges, we compute and aggregate sentence-level evidence to rank documents.
The lack of appropriate relevance judgments in test collections is addressed by leveraging sentence-level and passage-level relevance judgments fortuitously available in collections from other domains to capture cross-domain notions of relevance.
Our experiments demonstrate that models of relevance can be transferred across domains.
By leveraging semantic cues learned across various domains, we propose a model that achieves state-of-the-art results on three standard TREC newswire collections.
We explore the effects of cross-domain relevance transfer, and trade-offs between using document and sentence scores for document ranking.
We also present an end-to-end document retrieval system that integrates the open-source Anserini information retrieval toolkit, discussing the related technical challenges and design decisions.

\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

I would like to thank my advisor, Professor Jimmy Lin, for giving me the opportunity to work on exciting problems and to collaborate with inspiring researchers.
Without his continuing guidance and support, this thesis would not be possible.

I would like to thank the readers of my thesis, Professor Gordon V. Cormack and Charles L. A. Clarke, for reviewing my work.

I would like to thank Wei Yang, Haotian Zhang and Rodrigo Nogueira for their discussions and insights that contributed greatly to this thesis.

Finally, I would like to thank all the old and new friends who have made my time at the University of Waterloo an enjoyable experience.

\cleardoublepage

% D E D I C A T I O N
% -------------------

\begin{center}\textbf{Dedication}\end{center}

This is dedicated to my parents and to my husband, Goktug, for their unwavering love and support.

\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% GLOSSARIES (Lists of definitions, abbreviations, symbols, etc. provided by the glossaries-extra package)
% -----------------------------
\printglossaries
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

